The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts

### 2020-05-07 documents/paper.Rmd
fix 1985 text, which had a problem with PDF -> PNG conversion

---
title: "The Geometry of Archaeological Thought: ..."
output: bookdown::html_document2
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

@@

>>>>

---
title: "The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts"
output: bookdown::html_document2
bibliography: bibliography.bib
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

@@

The study of disciplinary change traditionally relies on close reading of a large number of publications, manually sorting them into pre-defined categories and making connections between these groups and external influences [e.g. @trigger1989history]. These methods are time-consuming and expensive, which excludes many people from participating. They are also vulnerable to biases

computational approaches that could scan the entire corpus to generate topics in a bottom-up fashion, based on the semantic content of the publications themselves. These approaches indeed make it possible to analyze more comprehensively and more systematically the contents of large corpora of full-text documents, be it in history and sociology
